---
title: "Content Access/Permissions Audit Report"
output: 
  html_document:
    theme: lumen
rmd_output_metadata:
  rsc_output_files:
    - "acl-detail-audit.csv"
---

`r if(Sys.getenv('CONNECT_SERVER') == '') { "<h4>ERROR: You must set the CONNECT_SERVER environment variable</h4>\n" }`
`r if(Sys.getenv('CONNECT_API_KEY') == '') { "<h4>ERROR: You must set the CONNECT_API_KEY environment variable</h4>\n" }`
`r if(Sys.getenv('CONNECT_API_KEY') == '' || Sys.getenv('CONNECT_SERVER') == '') { knitr::knit_exit() }`

**Generate a detailed list of all content items that have been shared with specific users or groups on RStudio Connect.** 

This report assumes you have already created Pins for the result of an administrator call to `/v1/content` (content enumeration), `/v1/users`, and `/v1/groups`.

## Get the Content List Pin

```{r echo=FALSE}
#
# ** BEFORE EXECUTING **
# - REPLACE PIN NAME 
# - REPLACE SERVER URL
#

# Register RStudio Connect
library(pins)
board_register("rsconnect", server = "YOUR-SERVER-URL")

# Retrieve Pin
content <- pin_get(name = "YOUR-PIN/content-info", board = "rsconnect")
```

Create a summary table of the number of content items under each access type.

- **`acl`** Access Control List - Specific users or groups
- **`logged_in`** All users - login required
- **`all`** Anyone - no login required

```{r access-summary, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(gt)

df <- content %>%
  select(guid, name, title, access_type, created_time, last_deployed_time, content_url, dashboard_url)

df %>% count(access_type, sort = TRUE) %>%
  gt() %>%
  tab_header(
    title = "Sharing Settings",
    subtitle = "RStudio Connect Server Content Audit"
  ) %>%
  cols_label(
    access_type = "Access Type",
    n = "Count"
  )
```

```{r include=FALSE}

# Filter content list by 'acl' access_type
acl_only <- df %>%
  filter(access_type == 'acl')
```


## Permissions API

```{r include=FALSE}
library(httr)

# Function for calling the content `/permissions` API endpoint
get_permissions <- function(guid) {
  permissions <- GET(paste0(Sys.getenv("CONNECT_SERVER"),"__api__/v1/content/",guid,"/permissions"),
    add_headers(Authorization = paste("Key", Sys.getenv("CONNECT_API_KEY"))))
  
  tidyr::unnest_wider(tibble::tibble(dat = content(permissions)), dat)
}

# Get permissions for all ACL-type content items
# Content that is accessible only by the publisher-owner (no additional users or groups) will return no records

acl_info <- lapply(acl_only$guid, get_permissions)
acl_tibble <- tidyr::unnest(tibble::tibble(dat = acl_info), dat)

# Calculate the number of content items accessible by the publisher-owner plus additional users or groups
acl_distinct <- acl_tibble %>% 
  select(content_guid) %>%
  n_distinct()
```

#### Content items accessible only by the publisher-owner (no additional users or groups): `r nrow(acl_only) - acl_distinct`

#### Content items accessible by a list of specific users or groups: `r acl_distinct` 

For each content item shared with additional specific users and groups, report the user/group and list whether they have viewer or collaborator access:

```{r echo=FALSE}
#
# REPLACE PIN NAMES BEFORE EXECUTING
# - user_list
# - group_list
#

library(reactable)

# Get the user info Pin
user_list <- pin_get(name = "YOUR-PIN/user-info", board = "rsconnect")

# Get the group info Pin
group_list <- pin_get(name = "YOUR-PIN/group-info", board = "rsconnect")

# Add user and group names to the permission info
acl_detail <- acl_tibble %>% 
  left_join(user_list, by=c("principal_guid" = "guid")) %>%
  left_join(group_list, by=c("principal_guid" = "guid")) %>%
  select(id, content_guid, principal_guid, principal_type, role, username, email, user_role, locked, name) %>%
  rename(group_name = name)

audit_table <- acl_detail %>%
  left_join(content, by=c("content_guid" = "guid")) %>%
  rename(content_name = name, 
         content_title = title,
         share_username = username,
         share_email = email,
         share_type = principal_type,
         share_role = role,
         share_group = group_name) %>%
  select(content_guid, content_title, dashboard_url, share_role, share_type, share_username, share_group)

reactable(audit_table, searchable = TRUE, highlight = TRUE, columns = list(
    content_guid = colDef(name = "GUID"),
    content_title = colDef(name = "Title"),
    dashboard_url = colDef(name = "Content URL", cell = function(value) {
    htmltools::tags$a(href = value, target = "_blank", "Link")
    }),
    share_role = colDef(name = "Access Type"),
    share_type = colDef(name = "User/Group"),
    share_username = colDef(name = "User Name"),
    share_group = colDef(name = "Group Name")
  ))
```

### Download the full report contents

```{r include=FALSE}

# Write the audit_table response out to a CSV file for download
write.csv(audit_table, "acl-detail-audit.csv", row.names=FALSE)
```

- Report: [acl-detail-audit.csv](acl-detail-audit.csv)
