---
title: "Vanity URL Audit Report"
output: 
  html_document:
    theme: flatly
rmd_output_metadata:
  rsc_output_files:
    - "vanity-url-audit.csv"
---

`r if(Sys.getenv('CONNECT_SERVER') == '') { "<h4>ERROR: You must set the CONNECT_SERVER environment variable</h4>\n" }`
`r if(Sys.getenv('CONNECT_API_KEY') == '') { "<h4>ERROR: You must set the CONNECT_API_KEY environment variable</h4>\n" }`
`r if(Sys.getenv('CONNECT_API_KEY') == '' || Sys.getenv('CONNECT_SERVER') == '') { knitr::knit_exit() }`

## List all defined vanity URLs on the RStudio Connect server

You must have administrator privileges to perform run this report.

[Requirements](https://docs.rstudio.com/connect/cookbook/#getting-started){target="_blank"}:

- [Administrator API Key](https://docs.rstudio.com/connect/user/api-keys/#api-keys-creating){target="_blank"} environment variable: `CONNECT_API_KEY`
- RStudio Connect server URL environment variable: `CONNECT_SERVER`

```{r content-list, include=FALSE}
library(httr)
library(tidyr)

# Use the /v1/vanities endpoint to list all vanity URLs
result <- GET(
  paste0(Sys.getenv("CONNECT_SERVER"),"__api__/v1/vanities"),
    add_headers(Authorization = paste("Key", Sys.getenv("CONNECT_API_KEY"))))

# Create a tibble for the vanity list result response
vanities <- unnest_wider(tibble::tibble(dat = content(result)), dat) 

vanities
```

### Download the full report contents

```{r include=FALSE}

# Write the full vanity URL list reponse out to a CSV file for download
write.csv(vanities, "vanity-url-audit.csv", row.names=FALSE)
```

- Report Data: [vanity-url-audit.csv](vanity-url-audit.csv)

---

### This server has `r nrow(vanities)` content items with assigned vanity URLs

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(reactable)

# Use reactable to create a nicely formatted table
reactable(vanities, searchable = TRUE, highlight = TRUE, columns = list(
  content_guid = colDef(name = "Content GUID"),
  path = colDef(name = "Path"),
  created_time = colDef(name = "Created", format = colFormat(datetime = TRUE))
))
```
