---
title: "Tag Usage Audit Report"
output: 
  html_document:
    theme: flatly
rmd_output_metadata:
  rsc_output_files:
    - "tag-list-audit.csv"
    - "tagged-content-audit.csv"
---

`r if(Sys.getenv('CONNECT_SERVER') == '') { "<h4>ERROR: You must set the CONNECT_SERVER environment variable</h4>\n" }`
`r if(Sys.getenv('CONNECT_API_KEY') == '') { "<h4>ERROR: You must set the CONNECT_API_KEY environment variable</h4>\n" }`
`r if(Sys.getenv('CONNECT_API_KEY') == '' || Sys.getenv('CONNECT_SERVER') == '') { knitr::knit_exit() }`

## List all the Tags on your RStudio Connect server & All tagged content

Authenticated access from an RStudio Connect user is required for `GET /v1/tags`.

[Requirements](https://docs.rstudio.com/connect/cookbook/#getting-started){target="_blank"}:

- [RStudio Connect API Key](https://docs.rstudio.com/connect/user/api-keys/#api-keys-creating){target="_blank"} environment variable: `CONNECT_API_KEY`
- RStudio Connect server URL environment variable: `CONNECT_SERVER`

```{r content-list, include=FALSE}
library(httr)
library(tidyr)
library(dplyr)

# Use the /v1/vanities endpoint to list all vanity URLs
result <- GET(
  paste0(Sys.getenv("CONNECT_SERVER"),"__api__/v1/tags"),
    add_headers(Authorization = paste("Key", Sys.getenv("CONNECT_API_KEY"))))

# Create a tibble for the tag list result response
tags <- unnest_wider(tibble::tibble(dat = content(result)), dat) 

# Filter the tibble to show just the parent tags
parent_tags <- tags %>%
  filter(is.na(parent_id))
```

### This RStudio Connect server has `r nrow(tags)` tags available in `r nrow(parent_tags)` tag categories

## List content for tags

Use the `GET /v1/tags/{id}/content` API endpoint to list all the content for a specified tag (id). 
_Note: Authenticated access from a user is required. If an "administrator" role is used, then all content items will be returned regardless of the visibility to the requesting user._

```{r include=FALSE}
# Get content items in each tag

# Function for calling the `GET /v1/tags/{id}/content` API endpoint
get_content <- function(id) {
  content_list <- GET(paste0(Sys.getenv("CONNECT_SERVER"),"__api__/v1/tags/",id,"/content"),
    add_headers(Authorization = paste("Key", Sys.getenv("CONNECT_API_KEY"))))
  
  tidyr::unnest_wider(tibble::tibble(dat = content(content_list)), dat) %>% 
    mutate(tag_id = {{id}})
}

tag_content <- lapply(tags$id, get_content)
tc_tibble <- tidyr::unnest(tibble::tibble(dat = tag_content), dat)

# Prepare a full list of tagged content items
# Join with the tags tibble

tags_tibble <- tags %>%
  rename(tag_id = id, tag_name = name, tag_parent = parent_id) %>%
  select(tag_id, tag_name, tag_parent)

tagged_content <- tc_tibble %>%
  left_join(tags_tibble)
```

### Download the full report contents

```{r include=FALSE}

# Write the full tag list reponse out to a CSV file for download
write.csv(tags, "tag-list-audit.csv", row.names=FALSE)

# Write the tagged content items out to a CSV file for download
write.csv(tagged_content, "tagged-content-audit.csv", row.names=FALSE)
```

- Tag List: [tag-list-audit.csv](tag-list-audit.csv)
- Tagged Content: [tagged-content-audit.csv](tagged-content-audit.csv)

---

### This RStudio Connect server has `r nrow(tags)` tags available

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

# Bar plot showing the Top 12 Content Tags
tagged_content %>% 
  count(tag_name, sort = TRUE) %>%
  top_n(12) %>%
  ggplot(aes(y = reorder(tag_name, n), x = n)) +
  geom_bar(stat = "identity") + 
  theme_minimal() + 
  labs(title = "Top 12 Content Tags",
       x = "Content Count",
       y = "Tag Name")+
  theme(plot.title.position = "plot")
```
