---
title: "Basic Audit Report"
output: 
  html_document:
    theme: lumen
rmd_output_metadata:
  rsc_output_files:
    - "rsc-basic-audit.csv"
---

## List all content items on the RStudio Connect server

To pull a complete list of the content items on your Connect server, you must use an API key generated from an Admin account. Publisher account API keys will only return content items which the publisher user has been given access to view or edit.

Requirements:

- [Administrator API Key](https://docs.rstudio.com/connect/user/api-keys/#api-keys-creating){target="_blank"}
- RStudio Connect server URL

```{r include=FALSE}
library(httr)
library(tidyr)

# Use the /v1/content endpoint to retrieve the full list of content items
result <- GET(
  paste0(Sys.getenv("CONNECT_SERVER"),"__api__/v1/content"),
    add_headers(Authorization = paste("Key", Sys.getenv("CONNECT_API_KEY"))))

# Create a tibble for the content list result response
df_full <- unnest_wider(tibble::tibble(dat = content(result)), dat) 
```

### Download the full report contents

```{r include=FALSE}

# Write the full content list reponse out to a CSV file for download
write.csv(df_full, "rsc-basic-audit.csv", row.names=FALSE)
```

- Report: [rsc-basic-audit.csv](rsc-basic-audit.csv)

---

## Explore the content list report

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(reactable)

# Filter the full response to select specific fields for viewing
df_view <- df_full %>%
  select(name, title, dashboard_url, app_mode, access_type, r_version, py_version, created_time, last_deployed_time)

# Use reactable to create a nicely formatted table
reactable(df_view, searchable = TRUE, highlight = TRUE, columns = list(
  name = colDef(name = "Name"),
  title = colDef(name = "Title"),
  dashboard_url = colDef(name = "Content URL", cell = function(value) {
    htmltools::tags$a(href = value, target = "_blank", "Link")
    }),
  app_mode = colDef(name = "Type"),
  access_type = colDef(name = "Access Level"),
  r_version = colDef(name = "R Version"),
  py_version = colDef(name = "Python Version"),
  created_time = colDef(name = "Created", format = colFormat(datetime = TRUE)),
  last_deployed_time = colDef(name = "Last Deployed", format = colFormat(datetime = TRUE))
))
```
